Timeliness of security updates for Android

### 2014-10-24 securityupdates.tex
More minor fixes

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frvh_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version\todo{make line of best fit thicker}}
 \label{fig:frvh_os_versions}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frms_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version}
 \label{fig:frms_os_versions}
\end{figure}

@@

The equation we chose for the model has a root mean squared error (RMSE) of \daOSCurveFitRMSE for OS versions, which is a comparably good fit to a standard polynomial fit (3 degree polynomial fit gave a RMSE of \daOSCurvePolyRMSE) or a spline fit (RMSE of \daOSCurveSplineRMSE) but gives a meaningful model of behaviour rather than a generic curve.

@@

@@

@@

Various attempts have been made to detect malware.
RiskRanker~\cite{Grace2012a} classified 3,281/118,318 (2.8\%) apps as risky of which 718 (22\%) were malware and 322 (10\%) were previously unknown, an infection rate of 0.6\% across multiple markets.
It uses signatures of exploits, static analysis of calls to high risk operations, detection of encrypted native code execution and dynamic Dalvik code loading to detect risky apps.
DroidRanger~\cite{Zhou2012a} found 148/182,823 (0.08\%) apps to be malicious across multiple markets of which 29 were previously unknown.
It used permission-based behavioural fingerprinting -- looking at the permissions of known malware and heuristic-based filtering -- dynamic loading of both Dalvik and native code.
AnDarwin~\cite{Crussell2013} detects similar apps, it found 169/265,359 (0.06\%) malicious apps based on the difference in permissions between the malicious app and the app which had been cloned.
It used clustering based on semantic vectors derived from the program dependence graphs to detect similar apps.
The Malware Genome project~\cite{Zhou2012b} collected 1,260 malware samples from 2010--2011.
They found that the best case for anti-malware detection on this data was 79.6\%.
However DroidChameleon~\cite{Rastogi2013} found that antivirus products could not detect malware if it was simply automatically permuted.
All these app analysis projects have been hampered by the difficulty of obtaining full datasets of Android apps as Google does not make these available (and researchers who automatically download them, violate Google's Terms of Service).
PlayDrone~\cite{Viennot2014} was a particularly effective project which circumvented Google's protective measures and downloaded over 1,100,000 apps from Google Play, allowing an in depth analysis.

>>>>

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frvh_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version\todo{make line of best fit thicker, I think the drops to 0 at the end of each version are erroneous}}
 \label{fig:frvh_os_versions}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/frms_os_versions}
 \caption{Proportion of devices not updated to particular versions of Android or any later version}
 \label{fig:frms_os_versions}
\end{figure}

@@

The equation we chose for the model has a root mean squared error (RMSE) of \daOSCurveFitRMSE\ for OS versions, which is a comparably good fit to a standard polynomial fit (3 degree polynomial fit gave a RMSE of \daOSCurvePolyRMSE) or a spline fit (RMSE of \daOSCurveSplineRMSE) but gives a meaningful model of behaviour rather than a generic curve.

\todo{Evaluate our model trained on the DA data against the ground truth Google Play data}

@@

We hope that a consequence of this paper will be a change in behaviour of the Android ecosystem which invalidates this model by speeding up the deployment of new OS versions.

@@

\subsection{Uncertainty propagation}

@@

Various attempts have been made to detect malware.
RiskRanker~\cite{Grace2012a} classified 3,281/118,318 (2.8\%) apps as risky of which 718 (22\%) were malware and 322 (10\%) were previously unknown malware, an infection rate of 0.6\% across multiple markets.
It uses signatures of exploits, static analysis of calls to high risk operations, detection of encrypted native code execution and dynamic Dalvik code loading to detect risky apps.
DroidRanger~\cite{Zhou2012a} found 148/182,823 (0.08\%) apps to be malicious across multiple markets of which 29 were previously unknown.
It used permission-based behavioural fingerprinting -- looking at the permissions of known malware and heuristic-based filtering -- dynamic loading of both Dalvik and native code.
AnDarwin~\cite{Crussell2013} detects similar apps, it found 169/265,359 (0.06\%) malicious apps based on the difference in permissions between the malicious app and the app which had been cloned.
It used clustering based on semantic vectors derived from the program dependence graphs to detect similar apps.
The Malware Genome project~\cite{Zhou2012b} collected 1,260 malware samples from 2010--2011.
They found that the best case for anti-malware detection on this data was 79.6\%.
However DroidChameleon~\cite{Rastogi2013} found that antivirus products could not detect malware if it was simply automatically permuted.
All these app analysis projects have been hampered by the difficulty of obtaining full datasets of Android apps as Google does not make these available (and researchers who automatically download them, violate Google's Terms of Service).
PlayDrone~\cite{Viennot2014} was a particularly effective project which circumvented Google's protective measures and downloaded over 1,100,000 apps from Google Play, allowing an in depth analysis.
